Portable Multi- and Many-Core Performance for Finite-Difference/Element Codes; Application to the Free-Surface Component of NEMO (NEMOLite2D 1.0).

### 2017-09-14 docs/papers/nemolite2d_performance/nemolite2d_perf.tex
nemolite2d-paper: update title and code DOI

\title{Portable Multi- and Many-Core Performance for Finite Difference Codes;
  Application to the Free-Surface Component of NEMO.}

@@

\codeavailability{The NEMOLite2D package is available as the GOcean
  2.0 benchmark, available from
  https://puma.nerc.ac.uk/trac/GOcean. Habakkuk is available from
  https://github.com/arporter/habakkuk.}

>>>>

\title{Portable Multi- and Many-Core Performance for Finite-Difference/Element Codes;
  Application to the Free-Surface Component of NEMO (NEMOLite2D 1.0).}

@@

\codeavailability{The NEMOLite2D Benchmark Suite 1.0 is available from
  the eData repository with DOI:
  http://dx.doi.org/10.5286/edata/707. Habakkuk is available from
  https://github.com/arporter/habakkuk.}
